Modeling Time-Variable Elemental Abundances in Coronal Loop Simulations

### 2024-05-09 src/tex/ms.tex
[showyourwork] overleaf sync

In a typical flare loop simulation, abundances are assumed to be photospheric, as this is what has been measured in the past (\textit{e.g.} \citealt{warren2014}).  However, more recent observations from X-ray spectrometers with high cadence and high spectral resolution have shown that the abundances vary rapidly with time \citep{mondal2021}, and for (relatively) small flares, a time-fixed photospheric abundance is overly simplistic.  Our simulations here show that large heating rates, as might be expected in the largest flares, do drive the abundances to photospheric values almost immediately.  However, for smaller heating rates, the abundance changes (due to flows, at least) do not reach photospheric values, and therefore the cooling rate of the loop is faster.  Of course, a real flare is not composed of a single loop, so this requires a multithreaded model to further investigate the observed time-dependence.

>>>>

In a typical flare loop simulation, abundances are assumed to be photospheric, as this is what has been measured in the past (\textit{e.g.} \citealt{warren2014}).  However, more recent observations from X-ray spectrometers with high cadence and high spectral resolution have shown that the abundances vary rapidly with time \citep{mondal2021}, and for (relatively) small flares, a time-fixed photospheric abundance is overly simplistic.  Recent spectroscopic observations have further found that post-flare coronal rain has photospheric abundances, while the host loop has coronal abundances \citep{brooks2024}, suggesting that the increase in density necessary to form that rain comes from material evaporated deep in the chromosphere.

Our simulations here show that large heating rates, as might be expected in the largest flares, do drive the abundances to photospheric values almost immediately.  However, for smaller heating rates, the abundance changes (due to flows, at least) do not reach photospheric values, and therefore the cooling rate of the loop is faster.  Of course, a real flare is not composed of a single loop, so this requires a multithreaded model to further investigate the observed time-dependence.  Additionally, a higher dimensional model is required to examine the formation of coronal rain, though rain is noticeably absent in ``standard'' flare loop modeling \citep{reep2020b}.
